Adaptive Scheduling of Scientific Workflows\\

### 2024-07-24 main.tex
literature search for competitor

        Polishedness scroe (how well-written is the chapter): 0 messy - 5 very clean.
        }
        TODO: Insert abstract
    \end{abstract}

@@

    \paragraph{HEFT-based algorithms}

    Introduced in 2002, HEFT~\cite{topcuoglu2002performance} has become a base for multiple heuristics in workflow (~\cite{SHI2006665, SANDOKJI2019482}) scheduling
    and in cloud-oriented environments(\cite{samadi2018eheft}).
    HEFT is even combined with reinforcement learning techniques(\cite{yano2022cqga}).

    HEFT-based or list-based heuristics are more applicable to very large workflows in comparison to greedy
    or exact algorithms(~\cite{de2012provenance},~\cite{rahman2013}).

    \paragraph{Memory-aware scheduling algorithms}
    Incorporating processor memory sizes into the scheduling problem is another layer of complexity in a scheduling problem.

    Different models of memory available on processors and memory requirements of tasks.
    The most straightforward memory representations assume no memory requirement on tasks of the workflow and single
    memories on each processor(\eg~\cite{rodriguez2019exploration}).
    In an assumed dual-memory systems(\cite{herrmann2014memory}) a processor can have access to a memory of two different kinds,
    and each task can be executed on one sort of memory.
    Cloud-oriented model can include costs associated with memory usage(\cite{liang2020memory}).

    The algorithm presented by Yao \etal~\cite{yao2022memory} looks similar to our heuristics on the first glance, but the
    model the authors adopt differs from the one assumed in this paper.
    The biggest difference is in the way processor memory is represented.
    In their model, each processor has an own internal memory and all processors share a common external one.
    The internal (local) memory is used to store the task files.
    The external memory is used to store evicted files to make room for the execution of a task on a processor.
    Yet, and this marks the decisive difference to our approach: once the files have been evicted into the communication
    buffer in our approach, they can only be transferred to another processor.
    In~\cite{yao2022memory}, in turn, the same processor can evict files and then take them back.
    This makes the approach not directly comparable with ours.
    Other differences in the model include edge weights in the workflow graph.
    Each edge in~\cite{yao2022memory} has two weights -- the size of the files transferred along it,
    and the time of communication along this edge, while we assume a single weight that represents file size and also
    determines the transfer time (along with the bandwidth).
    The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.
    They assume that the {\em minimum} local memory should be bigger than the memory requirement of the largest task.

\todo[inline]{TBD (HM): Still, wouldn't an empirical comparison make sense from a reviewer's point of view?}

    \paragraph{Dynamic case}
    Wang et al.~\cite{wang2019dynamic} proposes a dynamic particle swarm optimization algorithm to schedule workflows in a cloud.
    Particles are possible solution in the solution space.
    However, the dynamic is only in the choice of generation sizes, not in the changes in the execution environment.
    Singh et al.~\cite{singh2018novel} addresses dynamic provisioning of resources with a constraint deadline.
    However, the approach is for clouds.
    \xspace

@@

    De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling heuristic
    for clouds.
    Based on a 3-objective cost model, their greedy scheduling algorithm schedules tasks into machines.
    The authors use provenance data to make scheduling decisions.
    The cost model is a set of linear equations computed in the simulation environment, it represents the cost of an execution based on the criteria.
    In the algorithms, the authors test out 4 scenarios - one preferring each criteria, and a balanced one.
    The algorithm merely chooses the best virtual machine for each next task based on the cost given by the model.
    An additional algorithm combines several cloud activities (task executions) into one to improve the cost, so that each
    execution is not too small (utilize the granularity factor, the smallest entity of payment of the cloud producer).
    The authors used workflows with less than 10 tasks, but repeated them so that the execution had up to 200 tasks.
    They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.

    Rahman~\etal~\cite{rahman2013} propose a scheduling heuristic for grids that proposes mapping of tasks to machines by calculating
    the critical path in the graph dynamically at every step.
    They call it the dynamic critical path (DCP).
    For all tasks they compute the earliest start time and absolute latest start time that are upper and lower bounds
    on the start time of a task (differing by the slack this task has).
    All tasks on this critical path have the same earliest and latest start times, because they cannot be ddelayed.

    The algorithm takes the first unscheduled task on the critical path each time and maps it on a processor identified for it.
    If processors are heterogeneous, then the start times are computed with respect for the processor, and the minimum execution time for
    the task is chosen.
    The heuristic also uses the same processor to schedule parent and children tasks, as to avoid data transfer between processors.
    The authors evaluate their approaches on random workflows of the size up to 300 tasks.

    The authors provide an overview over (simpler) scheduling heuristics.
    For example, GRASP (generally randomized adaptive search procedure) conducts a number of iterations to search an optimal
    solution for mapping tasks on machines.
    A solution is generated at each step, and the best solution is kept at the end.
    The search terminates when a certain termination criterion is reached.
    It generates better results than other algorithms, because it explores the whole solution space.

    Avanes~\etal\cite{avanes2008adaptive} present a heuristic for networks in disaster scenarios.
    These networks are a set of DAG-shaped scenarios, out of which one needs to be executed.
    The scenario contains AND- and OR-branches, where AND-branches indicate acitivities that need to be executed in parallel.

    The heuristic first partitions the set into local schedules by using affinity matrices to determine similar
    activities and group them together.
    Then they physically allocate these partitions to groups of disaster responders and tasks within this group.
    They define a constraint system for that.
    The dynamic part deals with changes and distinguishes between retriable and compensation acitivities.
    The heuristic calculates a new execution path with these tasks.
    In general, this heuristic is not as related as it looks, because of very specific workflow and task structure.

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The aim is to minimize the makespan, and the experiments were conducted on a single wotkflow with 10 tasks.
    The procesdure involves building a first (static) schedule, priodic resource monitoring and rescheduling the remaining
    tasks.
    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
    For each resuorce group, there is an own scheduler, and an overall global scheduler responsible for distributing
    tasks to groups.
    The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

    The algorithm first computes bottom levels for all tasks (execution time is average of all possible execution times).
    THe bottom level represents the priority of the task, and tasks are sorted according to these priorities.
    They then go through tasks and map than to such processors that minimize the earliest start times of this task's
    successors.
    To do this, the authors calculate the earliest finishing time of the task across all ressources, along with the
    average communication and computation costs fir the dependent tasks.

    The rescheduling is being triggered when either a load on a resource increases over a threshold, or if a new resource
    is added.
    The algorithm produces a new mapping from scrath, and this mapping is being accepted if the resulting maespan is
    smaller than the previously predicted one.

@@

    \bibliographystyle{IEEEtran}
    \bibliography{references}

>>>>

        Polishedness score (how well-written is the chapter): 0 messy - 5 very clean.
        }
        TODO: Insert abstract
    \end{abstract}

@@

    We discuss relevant scheduling approaches that either reuse processors, or respect memory requirements of the processors.

    \subsection{Early list schedulers with unlimited processors}
    An entire cluster of works on list schedulers has been carried out as early as the 90s.
    They all assume a DAG-shaped workflow with makespan weights on tasks, and an unlimited amount of homogeneous processors
    with the speed of 1.

    The \textit{task duplication}-based approaches note that sometimes running a task twice on different machines can
    help reduce the makespan by saving communication costs.
    The two approaches are scheduling with the partial duplication~(SPD), and withe the full duplication~(SFD).
    For a join task (a task whose incoming degree is larger than its outgoing degree), SPD finds a critical immediate
    parent (the one that gives the largest start time to the join task) and duplicate only it.
    SFD duplicates all parents of a join node.
    \cite{dfrn1997} is a task duplication algorithm.
    The authors duplicate first (create copies of all parent tasks) and then reduce (remove) the ones that can be removed without harming
    the makespan.
    The critical path fast duplication algorithm \texttt{CPFD}~\cite{5727760} classifies tasks into three categories: a critical
    path task, and in-branch task, or out-branch task.
    It schedules critical path tasks first, then in-branch tasks.

    Linear clustering~\cite{KWOK1999381} acts on critical paths in the workflow.
    It assigns the current critical path to one processor, removes all these tasks from the workflow, recomputes the critical
    path and repeats the procedure.
    \texttt{Heaviest node first} algorithm~\cite{SHIRAZI1990222} assigns the tasks level by level, and in each level,
    schedules the heaviest (with largest computation time)  ones first.

    \subsection{Static list schedulers, especially HEFT-based algorithms}

    Introduced in 2002, HEFT~\cite{topcuoglu2002performance} is a list-based heuristic.
    It and all its successors consist of two phases: task ordering, and task assignment.
    In the first phase, the algorithms compute bottom levels of the tasks based on some priorities (create the list),
    and then schedule tasks in the order of these priorities.
    The modifications of HEFT revolve around the way the priorities of tasks are computed, and the logic
    of processor assignment.
    All such algorithms assume a heterogeneous execution environment.

    So, during task prioritization phase~\cite{sulaiman2021hybrid} compute the standard deviation of the computation cost
    (between processors) and add it to the mean value to account for the differences between processor speeds.
    In the processor choice phase, they duplicate the entry task and the longest parent tasks during idle times on the processor.

    \cite{alebrahim2017task} compute a the bottom level based on the difference of execution times on
    the fastest and the slowest processors, divided by the speedup (speeds ratio) of these two processors.
    When doing processor selection, the authors differentiate between the lowest execution time and earliest finishing time.
    They choose the processor with the lowest execution time, and cross over to other processors sometimes.
    They build upon~\cite{shetti2013optimization}.

    PEFT (Predict earliest finish time) algorithm~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table OCT.
    OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task, if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    Processor choice stage minimizes the Optimistic EFT, which is EFT plus the the longest path to the exit node for each task.

    The HSIP (Heterogeneous Scheduling with Improved task Priorities)~\cite{wang2016hsip} has an improved first step in
    comparison to HEFT.
    It combines the standard deviation with the communication cost weight on the tasks.
    In the second stage, the algorithm duplicates the entry task if there is a need for it.

    The TSHCS (Task Scheduling for Heterogeneous Comupting Systems) algorithm~\cite{alebrahim2017task} improves on HEFT
    by adding randomized decisions to the second phase.
    The decision is whether the task be assigned to the processor with the lowest execution time or to the processor that
    produces the lowest finish time.

    The \texttt{SDC} algorithm~\cite{SHI2006665} considers the percentage of feasible processors in addition to task’s
    average execution cost in its weight.
    The selected task is then assigned to a processor which minimizes its Adjusted Earliest Finish Time (AEFT) that
    additionally notes how large the communication between current node and its children will be on the
    average provided that it is scheduled on the current processor.

    HEFT  can also be adapted in cloud-oriented environments~\cite{samadi2018eheft} and even combined with reinforcement
    learning techniques(\cite{yano2022cqga}).

    \subsection{Memory-aware scheduling algorithms}
    Respecting processor memories adds a constraint to a scheduling problem.
    Therefore, only specifically memory-targeted algorithms address this issue.
    Moreover, the way processor memories are represented in the model has a decisive impact on the way the constraint
    is formulated and addressed in the algorithm.

    Different models of memory available on processors and memory requirements of tasks have been presented.

    Marchal~et~al.~\cite{marchal2018parallel} assume a memory model where each processor has an individual memory available.
    Workflow tasks have no memory requirements, but they have input and output files that need to be stored in the memory.
    A polynomial-time algorithm for computing the peak memory needed for a parallel execution of such a DAG is provided,
    as well as an ILP solution to the scheduling problem.
    The memory model requires deleting all input data upon starting of the task and adding all output files there.

    In an assumed dual-memory systems(\cite{herrmann2014memory}) a processor can have access to a memory of two different
    kinds (red or blue), and each task can be executed on only one sort of memory.
    The communications happen only between these two kinds of processors (communications withing each group are ignored).
    The authors then formulate an ILP solution for this problem formulation.

    The algorithm presented by Yao \etal~\cite{yao2022memory}, each processor has an own internal memory and all
    processors share a common external one. The internal (local) memory is used to store the task files.
    The external memory is used to store evicted files to make room for the execution of a task on a processor.
    All processors, including the original one, can access these files.
    Each edge in~\cite{yao2022memory} has two weights -- the size of the files transferred along it,
    and the time of communication along this edge.
    The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.

    \cite{ding2024ils} assumes connected processors with individual limited memories.
    The collective set of memories forms the global memory, to which each processor has access, however the access time
    to global memory is different.
    Each memory access in the graph is modelled as a memory access token on the task, while the edges have no weights.
    The solved problem is how to allocate initial input data in processor memories so that the overall
    execution is minimized and the memories are not exceeded.
    They propose an integer linear programming model.
    %that minimizes the length of the critical path, including a greedy initial solution.

    In~\cite{rodriguez2019exploration}, the authors assume memory requirement on tasks represented as tiles.
    Each processor has individual memories to process the task, but only the shared memories store the tiles containing
    memory tiles occupied by memory tiles.

    Cloud-oriented model can include costs associated with memory usage(\cite{liang2020memory}).

    \subsection{Dynamic/adaptive algorithms}

    DVR HEFT~\cite{SANDOKJI2019482} uses an almost unchanged HEFT algorithm in their static step, executing three slightly
    varying variants of task weighting and choosing the variant that gives the best overall makespan.
    In the dynamic phase, they receive new tasks and schedule them on either idle processors or those processors that give them
    the earliest finish time.
    Task failures are not covered.

    Rahman~\etal~\cite{rahman2013}'s dynamic critical path (DCP) algorithm for grids maps tasks to machines
    by calculating the critical path in the graph dynamically at every step.
    %For all tasks they compute the earliest start time and absolute latest start time that are upper and lower bounds
    %on the start time of a task (differing by the slack this task has).
    %All tasks on this critical path have the same earliest and latest start times, because they cannot be delayed.
    They schedule the first task on the critical path to the best suitable processor and recompute the critical path.
    %The algorithm takes the first unscheduled task on the critical path each time and maps it on a processor identified for it.
    %If processors are heterogeneous, then the start times are computed with respect for the processor, and the minimum
    %execution time for the task is chosen.
    The heuristic also uses the same processor to schedule parent and children tasks, as to avoid data transfer between processors.
    The approach is evaluated on random workflows of the size up to 300 tasks.

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The procedure involves building a first (static) schedule, periodic resource monitoring and rescheduling the remaining
    tasks.
    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
    For each resource group, there is an own scheduler, and an overall global scheduler responsible for distributing
    tasks to groups.
    The static heuristic is HEFT with earliest start time as priority.
    Upon rescheduling, a new mapping is calculated from scratch, and this mapping is accepted if the resulting makespan
    is smaller than the previous one.
    The experiments were conducted on a single workflow with 10 tasks.
%
    % The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    %The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

    %The algorithm first computes bottom levels for all tasks (execution time is average of all possible execution times).
    %THe bottom level represents the priority of the task, and tasks are sorted according to these priorities.
    %They then go through tasks and map than to such processors that minimize the earliest start times of this task's
    %successors.
    %To do this, the authors calculate the earliest finishing time of the task across all ressources, along with the
    %average communication and computation costs fir the dependent tasks.
    %
    %The rescheduling is triggered when either a load on a resource increases over a threshold, or if a new resource
    %is added.

    Most dynamic or adaptive algorithms are formulated for clouds, where the execution environment is not fixed,
    but constrained by cost.

    Wang et al.~\cite{wang2019dynamic} propose a dynamic particle swarm optimization algorithm to schedule workflows in a cloud.
    Particles are possible solution in the solution space.
    However, the dynamic is only in the choice of generation sizes, not in the changes in the execution environment.
    Similarly, Singh et al.~\cite{singh2018novel} addresses dynamic provisioning of resources with a constraint deadline.

    De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling algorithm
    for clouds.
    They solve a set of linear equations that represent the cost of an execution based on the criteria.
    The authors test out 4 scenarios - one preferring each criteria, and a balanced one.
    The algorithm chooses the best virtual machine for each next task based on the cost given by the model.
    The authors used workflows with less than 10 tasks, but repeated them so that the execution had up to 200 tasks.
    %They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.
 %   The authors use provenance data to make scheduling decisions.

@@

    \subsection{Other notable works}

    \cite{palis1996task} present a clustering-based scheduling algorithm for a parallel execution and prove its quality.
    They utilize task duplication when creating the clusters (grains).
    Their scheduler then maps clusters to processors.
    They assume unlimited processors with the speed of 1.
    For each task, they compute the earliest starting time and find a cluster, where this tasks's start time is as close
    to it as possible.
    %The cluster growing algorithm adds one task to the cluster at a time, by adding tasks in nondecreasing order of
    %release times.

    GRASP (generally randomized adaptive search procedure)~\cite{feo1989probabilistic} conducts a number of iterations
    to search for an optimal solution for mapping tasks on machines.
    A solution is generated at each step, and the best solution is kept at the end.
    The search terminates when a certain termination criterion is reached.
    It generates better results than other algorithms, because it explores the whole solution space.

    Avanes~\etal\cite{avanes2008adaptive} present a heuristic for networks in disaster scenarios.
    These networks are a set of DAG-shaped scenarios, out of which one needs to be executed.
    The scenario contains AND- and OR-branches, where AND-branches indicate activities that need to be executed in parallel.
    The heuristic first determines similar activities and groups them together.
    Then they allocate these groups to disaster responders and tasks within this group according to a constraint system.
    The dynamic part deals with changes and distinguishes between retriable and compensation activities.
    The heuristic calculates a new execution path with these tasks.

    \cite{lutke2024hetsim} is a scheduling simulator that models heterogeneous software with memory and accelerator
    (processor) speed heterogeneity.
    Each accelerator has its own memory that can be zero.
    Each accelerator's characteristics depend on the task it runs and are not fixed.

    \cite{meng2018traffic} investigate scheduling on multi-core chips.
    Their model is far from ours.

    An online scheduling algorithm~\cite{Witt2018POS} assumes a DAG-structured workflow and learns task characteristics.
    They prioritize tasks that have failed before or are well-predictable.

@@

    \bibliographystyle{apalike}
    \bibliography{references}
